### 2013-12-05 paper/main.tex
Direct Design working, major cleanup of Octave files
The first model has been built using Direct Design.
And it is a significant improvement compared to no control.

The Octave files used for generating the plots have been
cleaned up and their names made more consistent.

% {{{ fig:em_plot
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.7]{../octave/engine_model_plot}
\end{center}
\caption{Output response of engine model with no control.
The control can range from zero to one.
Here the control is constant at 0.65 which resulted in a stable
rpm near 900.}
\label{fig:em_plot}
\end{figure}
% }}}

@@

% {{{ fig:rpmtime_plot
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.7]{../octave/engine_model_rpmtime_plot}
\end{center}
\caption{Engine rpm response compared to time with a constant
0.65 input control.}
\label{fig:rpmtime_plot}
\end{figure}
% }}}

The response from zero rpm is not a realistic measurement of performance
because zero rpm is impossibly slow.
A typical idle rpm range is from 600 to 1000 rpm.
Figure \ref{fig:em_shift_plot2} shows the response for a step input
with control inputs chosen to reach 600 and 1000 rpm
\footnote{The control input to stable rpm values are given in
Appendix \ref{app:contrpm}}.
This is a more realistic representation of typical operation.
The rise time is near $0.2$ seconds and the overshoot is $15\%$.
And the stabilization time is almost one second.
Its behavior can still be improved with a controller.

% {{{ fig:em_shift_plot2
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.6]{../octave/em_shift_plot2}
\end{center}
\caption{Response for a shifted and scaled step input with zero torque.}
\label{fig:em_shift_plot2}
\end{figure}
% }}}

@@

% {{{ Pole Placement
\section{Pole Placement}

@@

Figure \ref{fig:cd1_plot} shows the response of this system given
an arbitrary input.
It can be seen that if the input is held constant the output (delta)
returns to zero as expected.

\begin{figure}[htbp!]
\includegraphics[scale=0.7]{../octave/cd1_plot}
\caption{Response of full steady state input to delta output system
to an arbitrary input signal.
The upper plot is the input signal ($u$) and the lower plot is
the output response ($y$).
The Matlab source code is given in Listing \ref{lst:cd1_init}
and \ref{lst:cd1_plot}.
}
\label{fig:cd1_plot}
\end{figure}

@@

It can be seen in Figure \ref{fig:cd2_plot} that the simplified system
behaves identically to the previous system (Figure \ref{fig:cd1_plot}).

\begin{figure}[htbp!]
\includegraphics[scale=0.7]{../octave/cd2_plot}
\caption{Response of simplified steady state input to delta output system
to an arbitrary input signal.
The upper plot is the input signal ($u$) and the lower plot is
the output response ($y$).
Response is identical to the full system in Figure \ref{fig:cd1_plot}
as expected.
The Matlab source code is given in Listing \ref{lst:cd2_init}
and \ref{lst:cd2_plot}.
}
\label{fig:cd2_plot}
\end{figure}

@@

\lstinputlisting[caption={Matlab code to initialize the full
steady state to delta system.},
	label=lst:cd1_init
	]{../octave/cd1_init.m}

\lstinputlisting[caption={Matlab code to plot the full steady state
to delta system.},
	label=lst:cd1_plot
	]{../octave/cd1_plot.m}

\clearpage
\lstinputlisting[caption={Matlab code to initialize the simplified
steady state to delta system.},
	label=lst:cd2_init
	]{../octave/cd2_init.m}

\lstinputlisting[caption={Matlab code to plot the simplified steady state
to delta system.},
	label=lst:cd2_plot
	]{../octave/cd2_plot.m}

@@

Figure \ref{fig:dc2_plot} shows the response of this system given
an arbitrary input
\footnote{This input is actually the output of the steady state input
to delta output given in Appendix \ref{app:cdelta}.
They are equal and opposite as expected.}.
It can be seen that the output is held in a steady state according
to the delta inputs as expected.

% {{{ fig:dc2_plot
\begin{figure}[htbp!]
\includegraphics[scale=0.7]{../octave/dc2_plot}
\caption{Response of delta input to steady state output system
when given an arbitrary input signal.
The upper plot is the input signal ($u$) and the lower plot is
the output response ($y$).
The Matlab source code is given in Listing \ref{lst:dc2_init}
and \ref{lst:dc2_plot}.
}
\label{fig:dc2_plot}
\end{figure}
% }}}

@@

%\lstinputlisting[caption={Matlab code to initialize the full
%steady state to delta system.},
%	label=lst:dc1_init
%	]{../octave/dc1_init.m}
%
%\lstinputlisting[caption={Matlab code to plot the full steady state
%to delta system.},
%	label=lst:dc1_plot
%	]{../octave/dc1_plot.m}

\lstinputlisting[caption={Matlab code to initialize the simplified
steady state to delta system.},
	label=lst:dc2_init
	]{../octave/dc2_init.m}

\lstinputlisting[caption={Matlab code to plot the simplified steady state
to delta system.},
	label=lst:dc2_plot
	]{../octave/dc2_plot.m}

@@

\lstinputlisting[
	caption={Matlab source to calculate the engine model system with
		zero torque.}
	]{../octave/engine_model.m}

\lstinputlisting[
	caption={Matlab source to plot the response of engine model
		with no control.}
	]{../octave/engine_model_plot.m}

% XXX
\clearpage
\lstinputlisting[
	caption={Matlab source to plot the response of engine model
		versus time.}
	]{../octave/engine_model_rpmtime_plot.m}

\clearpage
\lstinputlisting[
	caption={Matlab source to plot the response of engine model
		versus time for a shifted/scaled step input.}
	]{../octave/em_shift_plot2.m}
% }}}

\clearpage
\section{Control Response}
\label{app:contrpm}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.5]{../octave/stable_rpm_plot}
\end{center}
\caption{Stable rpm reached for a given constant control input.}
\label{fig:stable}
\end{figure}

\clearpage
\lstinputlisting[
	caption={Matlab source to find the stable rpm for a given
		control input with zero torque.},
	label={lst:stable}
	]{../octave/stable_rpm_plot.m}

>>>>

% {{{ fig:em_plot
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.7]{../octave/em_plot1}
\end{center}
\caption{Output response of engine model with no control.
The control can range from zero to one.
Here the control is constant at 0.65 which resulted in a stable
rpm near 900.}
\label{fig:em_plot}
\end{figure}
% }}}

@@

% {{{ fig:rpmtime_plot
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.7]{../octave/em_plot2}
\end{center}
\caption{Engine rpm response compared to time with a constant
0.65 input control.}
\label{fig:rpmtime_plot}
\end{figure}
% }}}

The response from zero rpm is not a realistic measurement of performance
because zero rpm is impossibly slow.
A typical idle rpm range is from 600 to 1000 rpm.
Figure \ref{fig:em_plot4} shows the response for a step input
with control inputs chosen to reach 600 and 1000 rpm
\footnote{The control input to stable rpm values are given in
Appendix \ref{app:contrpm}}.
This is a more realistic representation of typical operation.
The rise time is near $0.2$ seconds and the overshoot is $15\%$.
And the stabilization time is almost one second.
Its behavior can still be improved with a controller.

% {{{ fig:em_plot4
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.6]{../octave/em_plot4}
\end{center}
\caption{Response for a shifted and scaled step input with zero torque.}
\label{fig:em_plot4}
\end{figure}
% }}}

@@

% {{{ Direct Design
\section{Direct Design}

% {{{ fig:dd_plot2
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.7]{../octave/dd_plot2}
\end{center}
\caption{Output response of controller built using Direct Design
compared to no control.  For no control this is the same plot
as in Figure \ref{fig:em_plot4} which stabilizes after a second.}
\label{fig:dd_plot2}
\end{figure}
% }}}

@@

Figure \ref{fig:cd_plot1} shows the response of this system given
an arbitrary input.
It can be seen that if the input is held constant the output (delta)
returns to zero as expected.

\begin{figure}[htbp!]
\includegraphics[scale=0.7]{../octave/cd_plot1}
\caption{Response of full steady state input to delta output system
to an arbitrary input signal.
The upper plot is the input signal ($u$) and the lower plot is
the output response ($y$).
The Matlab source code is given in Listing \ref{lst:cd_plot1}.
}
\label{fig:cd_plot1}
\end{figure}

@@

It can be seen in Figure \ref{fig:cd_plot2} that the simplified system
behaves identically to the previous system (Figure \ref{fig:cd_plot1}).

\begin{figure}[htbp!]
\includegraphics[scale=0.7]{../octave/cd_plot2}
\caption{Response of simplified steady state input to delta output system
to an arbitrary input signal.
The upper plot is the input signal ($u$) and the lower plot is
the output response ($y$).
Response is identical to the full system in Figure \ref{fig:cd_plot1}
as expected.
The Matlab source code is given in Listing \ref{lst:cd_plot2}.
}
\label{fig:cd_plot2}
\end{figure}

@@

\lstinputlisting[caption={Matlab code to plot the full steady state
to delta system.},
	label=lst:cd_plot1
	]{../octave/cd_plot1.m}

\clearpage
\lstinputlisting[caption={Matlab code to plot the simplified steady state
to delta system.},
	label=lst:cd_plot2
	]{../octave/cd_plot2.m}

@@

Figure \ref{fig:dc_plot2} shows the response of this system given
an arbitrary input
\footnote{This input is actually the output of the steady state input
to delta output given in Appendix \ref{app:cdelta}.
They are equal and opposite as expected.}.
It can be seen that the output is held in a steady state according
to the delta inputs as expected.

% {{{ fig:dc_plot2
\begin{figure}[htbp!]
\includegraphics[scale=0.7]{../octave/dc_plot2}
\caption{Response of delta input to steady state output system
when given an arbitrary input signal.
The upper plot is the input signal ($u$) and the lower plot is
the output response ($y$).
The Matlab source code is given in Listing \ref{lst:dc_plot2}.
}
\label{fig:dc_plot2}
\end{figure}
% }}}

@@

\lstinputlisting[caption={Matlab code to plot the simplified steady state
to delta system.},
	label=lst:dc_plot2
	]{../octave/dc_plot2.m}

@@

\lstinputlisting[
	caption={Matlab source to calculate the engine model system with
		zero torque.  This function is called by other scripts that
	use this model.}
	]{../octave/engine_model.m}

\lstinputlisting[
	caption={Matlab source to plot the response of engine model
		with no control. The $x$ axis is in ticks.}
	]{../octave/em_plot1.m}

% XXX
\clearpage
\lstinputlisting[
	caption={Matlab source to plot the response of engine model
	with no control.  The $x$ axis is in time.}
	]{../octave/em_plot2.m}

\clearpage
\lstinputlisting[
	caption={Matlab source to plot the response of engine model
		versus time for a typical 600 to 1000 rpm range.}
	]{../octave/em_plot4.m}
% }}}

% {{{ Direct Design Matlab Source
\clearpage
\section{Direct Design Matlab Source}
\label{app:dd_matlab}

\lstinputlisting[
	caption={Matlab source used to plot the controller built using
	Direct Design compared to no control.}
	]{../octave/dd_plot2.m}

% {{{ Control Response
\clearpage
\section{Control Response}
\label{app:contrpm}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.5]{../octave/em_plot3}
\end{center}
\caption{Stable rpm reached for a given constant control input.}
\label{fig:stable}
\end{figure}

\clearpage
\lstinputlisting[
	caption={Matlab source to find the stable rpm for a given
		control input.},
	label={lst:stable}
	]{../octave/em_plot3.m}
% }}}
